---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# roxygenlabs

> Experimental 'roxygen' Tags and Extensions

[![Linux Build Status](https://travis-ci.org/gaborcsardi/roxygenlabs.svg?branch=master)](https://travis-ci.org/gaborcsardi/roxygenlabs)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/gaborcsardi/roxygenlabs?svg=true)](https://ci.appveyor.com/project/gaborcsardi/roxygenlabs)
[![](http://www.r-pkg.org/badges/version/roxygenlabs)](http://www.r-pkg.org/pkg/roxygenlabs)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/roxygenlabs)](http://www.r-pkg.org/pkg/roxygenlabs)

Experimental 'roxygen' Tags and Extensions

## Installation

Once on CRAN, install the package with

```r
install.packages("roxygenlabs")x
```

## Usage

Currently there is no official way to load a package when running
`devtools::document()` or `roxygen2::roxygenize()`, but you can use a trick:
put the package loading code into the `Roxygen` field in `DESCRIPTION`:

```
Roxygen: { library(roxygenlabs); list(markdown = TRUE) }
```

### Conditional examples

```{r child = "man/chunks/examplesIf.Rmd"}
```

### CSS and Javascript themes

```{r child = "man/chunks/theme.Rmd"}
```

## License

MIT © RStudio
